---
title: "HP aggression plot"
author: "MSCI 599"
output: html_document
---

### Demonstrate changing a repo forked from someone else's GitHub account

* We forked the Harry-Potter-aggression repo from GitHub user andrewheiss
* We cloned our version of the repo to our local computer and put it in a version-controled RStudio project
* We can add files, make changes, etc., and push them back to our GitHub repo

### Work with the HP data

Load packages and data
```{r, include = FALSE}
library(tidyverse)
hp_data = read_csv("harry_potter_aggression_full.csv")
```

Filter out all characters except Harry and Malfoy, and plot their aggressions per book:

```{r}
hp_simple = hp_data %>% 
  filter(Name == "Harry" | Name == "Draco Malfoy") %>% 
  select(Name, book, agg.per.mention)

ggplot(aes(x = book, y = agg.per.mention), data = hp_simple) +
  geom_col(aes(fill = Name), position = "dodge") +
  coord_flip() +
  labs(x = "", y = "Aggressions per mention") +
  theme_bw() +
  scale_y_continuous(expand = c(0,0))
```

### Acknowledgements

From Allison Horst's GitHub tutorial:
https://github.com/allisonhorst/esm-206-2018/tree/master/week_6